Software architectures to integrate workflow engines in science gateways

### 2016-10-12 answers.tex
Still more answers to the reviewers

  As discussed previously, we share the reviewer's concerns
  about the feasibility of workflow conversion (see comments on
  interaction (g) in Section 5.2). The performance of workflow
  conversion is strongly related to the availability of a validated
  interaction (g), which is very dependent on the particular workflow
  engines under consideration. We believe that the issue raised by the
  reviewer basically comes down to the weight given to software
  components and interactions in the analysis. However, using
  different weights for different components or interactions would
  open an infinite number of configurations for discussion. For
  instance, in some cases, the workflow engine already comes with a
  workflow service which therefore doesn't have to be included. To
  address this issue, we shared a spreadsheet at
  \url{https://frama.link/LrPRsCQp} that allows editing the following
  weights:
  \begin{itemize}
  \item Weight given to software components and interactions in
  ``integration'', ``extensibility'' and ``robustness'' criteria.
  \item Weight given to metrics in a criterion (e.g., E$_1$ vs. E$_2$ in
  ``extensibility'').
  \item Weight given to criteria in overall evaluation of Table 3.
\end{itemize}
The paper references this spreadsheet wherever equal weights are
assumed. The readers and reviewers are invited to rely on this
spreadsheet for any issue related to the importance given to a
specific component, interaction, metric or criterion in the
analysis. In the paper, we assumed that all weights equal 1, which we
believe is a reasonable but limited choice.

@@

@@

\todo{Don't divide by the total number of interactions because then a
  given interaction could have a different value depending on the
  architecture. Refer to spreadsheet where weights can be adjusted.}

@@

\todo{OK but these components are not specific to workflow
  execution. So it's out of the definition. Motivation for this definition: these components are here anyway. If the SG fails, then the
  workflows can't even be started. If the infrastructure is down, same. }

@@

\todo{no, because c1 is not red.}

@@

\todo{I agree it's boring but it's also important to have it clearly written.}

@@

\todo{what???}

@@

>>>>

  As discussed previously, we share the reviewer's concerns
  about the feasibility of workflow conversion (see comments on
  interaction (g) in Section 5.2). The performance of workflow
  conversion is strongly related to the availability of a validated
  interaction (g), which is very dependent on the particular workflow
  engines under consideration. We believe that the issue raised by the
  reviewer basically comes down to the weight given to software
  components and interactions in the analysis. However, using
  different weights for different components or interactions would
  open an infinite number of configurations for discussion. For
  instance, in some cases, the workflow engine already comes with a
  workflow service which therefore doesn't have to be included. To
  address this issue, we shared a spreadsheet at
  \url{https://frama.link/LrPRsCQp} that allows editing the following
  weights:
  \begin{itemize}
  \item Weight given to software components and interactions in
  ``integration'', ``extensibility'' and ``robustness'' criteria.
  \item Weight given to metrics in a criterion (e.g., E$_1$ vs. E$_2$ in
  ``extensibility'').
  \item Weight given to criteria in overall evaluation of Table 3.
\end{itemize}
The paper references this spreadsheet wherever equal weights are
assumed. The readers and reviewers are invited to rely on this
spreadsheet for any issue related to the importance given to a
specific component, interaction, metric or criterion in the
analysis. In the paper, we assumed that all weights equal 1, which we
believe is a reasonable choice although inherently limited.

@@

\begin{answer}
As suggested by the reviewer, the presentation of these Figures has been gathered in a separate section, the new section 3.
\end{answer}

@@

\begin{answer}
  We agree with the reviewer that different weights could be given to
  interactions and software components depending on the ``gravity'' of
  the associated failures, the ``difficulty'' to repair them and even
  the difficulty to implement such interactions and components in
  practice (for instance, interaction \texttt{g} is clearly very
  difficult to implement).

  However, we believe that assigning such weights is specific to the
  case of a particular system, i.e. a science gateway and workflow
  engine(s). Very different ponderations could be obtained depending
  on the technical context, for instance implementation language, type
  of targeted infrastructure (dedicated cluster vs. grid vs. cloud)
  and characteristics of the workflow engine(s) and language(s).

  Instead, we shared a spreadsheet at
  \url{https://frama.link/LrPRsCQp} that allows editing the following
  weights (see also answer to Reviewer \#1):
  \begin{itemize}
  \item Weight given to software components and interactions in
  ``integration'', ``extensibility'' and ``robustness'' criteria.
  \item Weight given to metrics in a criterion (e.g., E$_1$ vs. E$_2$ in
  ``extensibility'').
  \item Weight given to criteria in overall evaluation of Table 3.
\end{itemize}
The paper references this spreadsheet wherever equal weights are
assumed. The readers and reviewers are invited to rely on this
spreadsheet for any issue related to the importance given to a
specific component, interaction, metric or criterion in the
analysis. In the paper, we assumed that all weights equal 1, which we
believe is a reasonable choice although inherently limited.

We find the particular ponderation method suggested by the reviewer
(normalization by the number of components or interaction in the
architecture) a bit unfortunate because it would give different
ponderations to the same component or interaction depending on the
architecture in which it is used, which we think would obfuscate the
comparison.
\end{answer}

@@

\begin{answer}
  We believe that the robustness of a system for a particular function
  should be evaluated w.r.t the set of components and interactions
  that are \emph{specific} to this function. Indeed, the failure of
  non-specific components is likely to impact many other functions
  that are required by the particular function of interest. To take an
  extreme example, a failure of the internet connection of the gateway
  user would certainly prevent him/her to launch a new workflow, but
  it does not really make sense to integrate the internet connection
  in the robustness analysis because it is not specific to workflow
  execution. Similarly, the failure of the science gateway would
  prevent users to login in the first place, which would prevent
  workflow execution in any case. Likewise, the failure of the
  infrastructure would make any workflow execution worthless in any
  architecture because infrastructure is used for other critical
  functions such as task execution and data storage.

  For these reasons, we disagree with the suggestion made by the
  reviewer. In any case, science gateway and infrastructure are
  present in all the architectures, which would only add 2 to all the
  values of R1.
\end{answer}

@@

\begin{answer}
  In Figure 2.I, interaction \texttt{c$_1$} is not specific to
  workflow execution since it is used to transfer any data to the
  infrastructure. This is why we don't count it in R2, for the same
  reason as explained previously.
\end{answer}

@@

\begin{answer}
  While we agree that the Sub-Sections in Section 3 look a bit
  repetitive, we believe that the metrics evaluation reported in Table 2 needs to be
  properly justified. 
\end{answer}

@@

\begin{answer}
  Service invocation and Task encapsulation are fundamentally different for the following reasons:
  \begin{itemize}
  \item In task encapsulation, the workflow engine runs on the infrastructure while in service invocation, it is hosted by a dedicated service.
  \item In task encapsulation, the workflow engine is executed as a task of the infrastructure while in service invocation, it is invoked through a service call. That means, in particular, that in task encapsulation different workflow engines are executed through the same protocol (a task), while different types of service calls might be involved in service invocation (e.g. REST or SOAP Web-Service).
  \item In task encapsulation, the workflow engine does not transfer data to the infrastructure while in service invocation it does (interactioni \texttt{c$_2$}.
  \item In task encapuslation, the science gateway submits tasks to the infrastructure, while in service invocation the workflow engine does.
  \end{itemize}
  Therefore, while we acknowledge that task encapsulation and service
  invocation share characteristics, we believe that their differences
  can be clearly inferred from section 2 of the paper. 
\end{answer}

@@

\todo{ponderation again}
